### 2024-06-02 2024-5-13/sections/implementation.tex
correct the description of complement instances in NestC benchmark suite

\medskip
\noindent
\emph{NestC benchmark suite.} 
\zhilin{To be cleaned}
This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator. We generate 500 instances of the nesting of counting operators containing the RECL constraint $x\in e_{nest}\wedge x\in e_{sani}\wedge |x|>50$ in each of them, where $e_{nest}\equiv (e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}})^{\{m_4,n_4\}}$ is a regex of the nesting of counting operators and $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is as RegCoL benchmark suite. Note that $0\leq m_i\leq n_i\leq 20$ for $i\in [4]$ and $e_i$ containing no counting operators for $i\in [3]$ is randomly generated.  We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{nest}\wedge x\in e_{comp} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{nest}$ and $e_{sani}$ are as above. Note that $20\leq m_i\leq n_i\leq 1000$ and $e_i$  containing no counting operators for $i\in [3]$ is randomly generated.

@@

The experiment results can be found in Table~\ref{tab:results_algorithm}. From the results, we can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than $\ostrichrecl_{\rm +NUXMV}$. 
Therefore, the technical choice in Section~\ref{sec:algorithm} where LIA formulas are computed and then solved by the SMT solvers is reasonable, since $\ostrichrecl$ with this technical choice is more efficient than $\ostrichrecl_{\rm +NUXMV}$, where nuXmv is used to solve the $\cefadec$ problem. 
%
Moreover, $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than $\ostrichrecl_{\rm -ASR}$. 
From the results, we can see that the automata-size reduction technique indeed plays an important role for the performance improvement. 
%
\begin{table}
  \import{tables}{table_algorithm.tex}
  \caption{Evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}\label{tab:results_algorithm}
\end{table}

>>>>

\medskip
\noindent
\emph{NestC benchmark suite.} 
\zhilin{To be cleaned}
This benchmark suite is generated by string fuzzing test tool \textsc{stringfuzz} \cite{stringfuzz} extended with the counting operator. We generate 500 instances of the nesting of counting operators containing the RECL constraint $x\in e_{nest}\wedge x\in e_{sani}\wedge |x|>50$ in each of them, where $e_{nest}\equiv (e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}})^{\{m_4,n_4\}}$ is a regex of the nesting of counting operators and $e_{sani} \equiv \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*}$ is as RegCoL benchmark suite. Note that $0\leq m_i\leq n_i\leq 20$ for $i\in [4]$ and $e_i$ containing no counting operators for $i\in [3]$ is randomly generated.  We also generate 500 instances of the nesting of counting operators and a complement operator containing the RECL constraint $x\in e_{comp1}\wedge x\in e_{comp2} \wedge x\in e_{sani} \wedge |x|>50$ in each of them, where $e_{comp\{1,2\}}\equiv \overline{e_0^{\{m_0,n_0\}}e_1^{\{m_1,n_1\}}e_2^{\{m_2,n_2\}}e_3^{\{m_3,n_3\}}}$ is a regex of the nesting of counting operators and a complement operator, and $e_{sani}$ are as above. Note that $20\leq m_i\leq n_i\leq 1000$ and $e_i$  containing no counting operators for $i\in [3]$ is randomly generated.

@@

The experiment results can be found in Table~\ref{tab:results_algorithm}. From the results, we can see that $\ostrichrecl$ solves 2,532 more instances and is 2.38 times faster than $\ostrichrecl_{\rm +NUXMV}$. 
Therefore, the technical choice in Section~\ref{sec:algorithm} where LIA formulas are computed and then solved by the SMT solvers is reasonable, since $\ostrichrecl$ with this technical choice is more efficient than $\ostrichrecl_{\rm +NUXMV}$, where nuXmv is used to solve the $\cefadec$ problem. 
%
Moreover, $\ostrichrecl$ solves 1,083 more instances and is 1.65 times faster than $\ostrichrecl_{\rm -ASR}$. 
From the results, we can see that the automata-size reduction technique indeed plays an important role for the performance improvement.

\begin{table}
  \import{tables}{table_algorithm.tex}
  \caption{Evaluation of the technical choices and optimizations in Section~\ref{sec:algorithm}}\label{tab:results_algorithm}
\end{table}
